Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-11 write_up/Supplementary.tex
Final bits reviewers comments

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years are the light grey
		lines, the mean of all years the thick black line.}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 1) for 52 separate weeks.}
	\label{fig:5}
\end{figure}

@@

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 2) for 52 separate weeks.}
	\label{fig:6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_3}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 3) for 52 separate weeks}
	\label{fig:7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
	\caption{Spawning habitat preference: the habitat suitability during
		spawning periods for each population.}
	\label{fig:2}
\end{figure}

>>>>

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		aggregated across the entire spatial domain showing weekly and
		seasonal patterns in exploitation. Individual years are the
		light grey lines, the mean of all years the thick black line.}
	\label{fig:10}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
	\caption{Spawning habitat preference: the habitat suitability during
		spawning periods for each population. The darker the colour,
		the more suitable the habitat. The location of the spawning
		habitat is highlighted by the squares in each panel.}
	\label{fig:2}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 1) for 52 separate weeks. The darker the
		colour, the more suitable the habitat for the population given
	the habitat and temperature tolerance.}
	\label{fig:5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 2) for 52 separate weeks. The darker the
		colour, the more suitable the habitat for the population given
	the habitat and temperature tolerance.}
	\label{fig:6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_3}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 3) for 52 separate weeks. The darker the
		colour, the more suitable the habitat for the population given
	the habitat and temperature tolerance.}
	\label{fig:7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 4) for 52 separate weeks. The darker the
		colour, the more suitable the habitat for the population given
	the habitat and temperature tolerance.}
	\label{fig:8}
\end{figure}

### 2020-01-11 write_up/mixfishsim_ecolmod_revisions.tex
Final bits reviewers comments

There is increasing interest in technical solutions such as gear and spatial
closures as measures to reduce unwanted catch \citep{Kennelly2002,
	Catchpole2008, Bellido2011, Cosgrove2019} and adaptive spatial
management strategies have been proposed as a way of reducing over-quota
discards \citep{Holmes2011, Little2014, Dunn2014a}. However, if fisheries are
to reduce unwanted catch through spatial avoidance, an in-depth understanding
of spatiotemporal fishery dynamics is required. \\

>>>>

There is increasing interest in technical solutions such as gear and spatial
closures as measures to reduce unwanted catch\added{ which is often discarded}
\citep{Kennelly2002, Catchpole2008, Bellido2011, Cosgrove2019}\added{.
	A}\deleted{ and a}daptive spatial management strategies have been
proposed as a way of reducing over-quota discards \citep{Holmes2011,
	Little2014, Dunn2014a}. However, if fisheries are to reduce unwanted
catch through spatial avoidance, an in-depth understanding of spatiotemporal
fishery dynamics is required. \\
